\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-17 doc/mlsys_paper/paper.tex

% I guess to save some space we should group them.
%% CS: should we add citations to some (or all) of the listed optimisers?
%% CS: the MLSYS CFP states that "papers can be up to 6 pages (not including references)",
%% CS: so technically we can have 10000+ references.
\vspace*{-0.4em}
\begin{enumerate}[{~~~$\bullet$}]
\small
  \item {\bf SGD variants:}
      Stochastic Gradient Descent (SGD),
      SGD with Restarts,
      Parallel SGD (Hogwild!),
      Stochastic Coordinate Descent, 
      SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

  \item {\bf Quasi-Newton variants:} Limited-memory BFGS (L-BFGS), incremental
        Quasi-Newton method, Augmented Lagrangian Method

  \item {\bf Genetic variants:} Conventional Neuro-evolution, Covariance
        Matrix Adaptation Evolution Strategy

  \item {\bf Other:} Conditional Gradient Descent, Frank-Wolfe algorithm, Simulated Annealing

>>>>

% I guess to save some space we should group them.
%% CS: should we add citations to some (or all) of the listed optimisers?
%% CS: the MLSYS CFP states that "papers can be up to 6 pages (not including references)",
%% CS: so technically we can have 10000+ references.
\vspace*{-0.4em}
\begin{enumerate}[{~~~$\bullet$}]
\small
  \item {\bf SGD variants}~\cite{Robbins_1951,kingma2015adam}:
      Stochastic Gradient Descent (SGD),
      SGD with Restarts,
      Parallel SGD (Hogwild!),
      Stochastic Coordinate Descent, 
      SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

  \item {\bf Quasi-Newton variants}:
      Limited-memory BFGS (L-BFGS)~\cite{zhu1997algorithm},
      incremental Quasi-Newton method~\cite{Mokhtari_2018},
      Augmented Lagrangian Method~\cite{Hestenes_1969}

  \item {\bf Genetic variants}:
        Conventional Neuro-evolution,
        Covariance Matrix Adaptation Evolution Strategy

  \item {\bf Other}: Conditional Gradient Descent, Frank-Wolfe algorithm, Simulated Annealing~\cite{kirkpatrick1983optimization}
